### 2016-11-20 src/local.tex
trying to merge

The local search algorithm maintains a feasible matching throughout its execution
and operates in 
iterative manner where in each iteration it tries to find a better solution by
replacing a subset of the edges in the current solution with 
another (larger) subset of edges not in the solution.
The local search algorithm halts when no improvement can be done.
The algorithm is described in Algorithm~\ref{alg:local}

@@

We claim that the local search algorithm halts in polynomial time.
Observed that in every iteration the algorithm either improves the value of the solution
by one or otherwise it terminates. 
Thus, after a maximum of $n$ iterations the algorithm stops.
In every iteration we examine all the subsets of edges of a fixed size and test for feasibility,
both these operations can be done in polynomial time - $O(n^{Ck + 1})$.

To analyze the approximation ratio achieved by the local search algorithm consider an 
arbitrary but fixed optimal matching $M^* = \{s_1, \ldots, s_m\}$,
where $s_1, \ldots, s_m$ are the stars induced by the optimal solution.
Given the solution outputted by the local search algorithm,
we build the \emph{conflict graph} of the two solutions in which each node
represents a star from the optimal solution and edges exits between two nodes if
the local search solution has at least one edge that connects two stars, formally 
$G_\text{conflict} = (V, E)$ 
where $\{v_i : s_i \in M^* \}$ 
and $E = \{(v_i, v_j) : \exists (u,v) \in M \land u \in s_i, v \in s_j \}$.
Denote by $d^*_i$ the sum of the vertex degree of the optimal solution in $s_i$, 
and by $d_i$ the sum of the vertex degree of the local search solution in $s_i$.

\begin{figure}[h]
\centering
\input{fig-conflict}
\caption[]{
\label{fig:carpool}
A carpool matching example: 
\subref{subfloat:input} 
a directed graph with capacities on the vertices and weights on the edges. 
\subref{subfloat:output}
a feasible matching with total weight of 26.
$P$ is the set of blue vertices, and $D$ is the set of red, dashed vertices. 
}
\end{figure}

>>>>

The local search algorithm maintains a feasible matching throughout its execution
and operates in 
iterative manner where in each iteration it tries to find a better solution by
replacing a subset of the edges in the current solution with 
another (larger) subset of edges not in the solution.
The local search algorithm halts when no improvement can be done.
The algorithm is described in Algorithm~\ref{alg:local}.

@@

We claim that the local search algorithm terminates in polynomial time.
Observed that in every iteration the algorithm either improves the value of the solution
by one or otherwise it stops. 
Thus the algorithm stops after $n$ iterations at most.
Finally, 
in every iteration we examine all the subsets of edges of a fixed size 
and test for feasibility.
Both these operations can be done in polynomial time - $O(n^{Ck + 1})$.

For two sets of stars $S^*, S$ on a common ground set of vertices $V(G)$,
define the conflict graph $G^{S^*}_{S} = (V, E)$
where $V = \{v_i : s_i \in S^*\}$, 
and $E = \{(v_i, v_j) : 
\exists s \in S : 
\{v_i, v_j\} \subseteq V(s) 
\}$.
Let $w^*(v_i) = 2|E(s_i|$, 
and let $w(v_i)$ be the sum of degrees (in and out) induced by $S$ on vertices in $s_i$. 
That is, the stars in $S^*$ define the vertices in the conflict graph,
and two vertices in the conflict graph are adjacent if there is a star in 
$S$ that intersect the two corresponded stars in $G$.
Figure~\ref{fig:conflict} depicts these concepts.

\begin{figure}[h]
\centering
\subfloat[]{
\label{subfloat:graph}
\input{fig-sub-graph}
}
\subfloat[]{
\label{subfloat:conflict}
\input{fig-sub-conflict}
}
\caption[]{
\label{fig:conflict}
\subref{subfloat:graph}
Two sets of stars, 
$S^* = \{\{a,b,c\}, \{d,e,f\}, \{h,i,j\}, \{k,l\}\}$, 
$S = \{\{a,h\}, \{c,j\}, \{b,e\}\}$ 
\subref{subfloat:conflict}
The conflict graph $G^{S^*}_{S}$, the upper left vertex corresponds 
to the star \{a,b,c\}.
The numbers on each vertex $v$ represent the value of $w(v)$.
}
\end{figure}

It is easy to verify the following observation regarding the conflict graph.

\begin{observation}  
The degree of every vertex $v \in V$ is at most $w(v)$.
\end{observation}

For a subset $U \subset V$ let $S^*(U)$ be the set of stars corresponds to 
the vertices in $U$,
$V_U = V(S^*(U))$,
$\overline{V_U} = V(G) \setminus V_U$,
$E^{S^*}_U = E(S^*) \cap V_U \times V_U$,
and 
$E^{S}_U = E(S) \cap V_U \times V_U$.
When $U$ is the set of vertices of a maximal connected component of a conflict graph,
then it is easy to verify that the following observations hold.

\begin{observation}  
$|E^{S}_U| = \frac{1}{2} \sum_{u \in U} w(u)$.
\end{observation}

\begin{observation}  
$|E^{S^*}_U| = \frac{1}{2} \sum_{u \in U} w^*(u) \leq |U| \cdot C$.
\end{observation}

Let $M^*$ be an arbitrary but fixed optimal star family in $G$, 
and let $M$ be the output of the local search algorithm,  
and consider the conflict graph $G^{M^*}_M = (V,E)$,
and let $U$ denote the vertices of a maximal connected component in $G^{M^*}_M$
of size at most $|U| \leq k$ then the following holds:

\begin{observation}
$w^*(U) = w(U)$.
\end{observation}

\begin{proof}
Clearly, $E(S) \cap  V_U \times \overline{V_U} = \emptyset$,
or else this is not a maximal connected component in $G^{M^*}_M$.
If $w^*(U) \neq w(U)$ 
the local search algorithm can improve the solution by
replacing the edges $E^{S}_U$ with the edges $E^{S^*}_U$. 
\end{proof}

Let $U$, now, represent the vertices of any connected subgraph of $G^{M^*}_M$
of size $k$, then:

\begin{observation}
$w^*(U) = w(U)$.
\end{observation}

\begin{theorem}
The local search is a $\frac{C + 1}{2C}$-approximation algorithm.
\end{theorem}

\begin{proof}
Let $M^*$ be an arbitrary but fixed optimal matching and let $M$ be the matching from the 
local search algorithm.
Consider the conflict graph.
\end{proof}
